### 2017-01-11 doc/manuscript.Rmd
First (rough) draft of intro

- TAG strong predictor of diabetes and CVD risk
- Not well studied how composition plays a role
- Limited longitudinal data

Our objective was to examine the longitudinal role of the specific composition
of the TAG serum fraction on OGTT-derived measures of insulin sensitivity and
beta-cell function.

NEFA may be a mediating factor in association, but that adjustment will not
attenuate this assoc since TAGFA composition is also dictated by other sources
for DNL (e.g. recent meal, DNL from glucose stores, etc.).

>>>>

Hypertriglyceridemia is an established and well known factor involved in the
dysregulation of metabolic function and subsequent negative health impacts. It
is a component of the metabolic syndrome {{ cite }}, a strong risk factor for
cardiovascular disease {{cite}}, and can contribute to worsening pathogenesis of
diabetes through it's harmful health effects {{ clarify }}. Triacylglcerol (TAG)
is a common blood measure taken during routine clinical visits and has {{
historically?}} been a target of pharmaceutical intervention {{cite}}, though evidence on
the {{efficacy? effectiveness?}} of such interventions are often underwhelming
on their effects on disease {{risk?}} reduction {{cite}}.

TAG as a pharmaceutical target and as a measure of metabolic health is a single
measure of all fatty acids within the TAG fraction. However, given the 
increasing appreciation for the role of the specific fatty acid (FA) composition
of various blood lipid fractions on health outcomes, reducing the complex FA 
metabolism within the TAG fraction to a single measure may contribute to the 
less than expected {{?}} changes in risk reduction.

In additiona, the {{interplay?}} between TAG and IR is complex and has the
potential to act as a {{feed forward?}} loop. Greater resistance to insulin,
particularly in the liver, can result in greater accumulation of hepatic fat and
a potential associated increased production in TAG which are secreted into
circulation with VLDL [@Yu2012a] {{review on mechanisms of TAG, IR, etc.}} {{not
always the case, dependent on ethnicity}}. However, higher circulating TAG can
exacerbate or contribute to insulin resistance in various tissues, creating a
vicious cycle {{cite}}. Few studies have been conducted that have examined the
longitudinal effect of TAGFA composition on diabetes pathophysiology.

Several prospective studies have identified to date the association of 
hypertriglyceridemia on incident diabetes {{[@Chien2008a; @DAgostino2004a;
@Schulze2009a]}}, but no longitudinal studies have been conducted{{another 
word?}} on the pathophysiological factors underlying diabetes.

Our objective was to examine the longitudinal role of the specific composition
of the serum TAG fraction on OGTT-derived measures of insulin sensitivity and
beta-cell function in an Canadian population at risk for diabetes over 6 years.
